A* with Fast and Tight Heuristic in Road Networks

### 2020-08-13 paper/ch_potentials.tex
move truck routing from related work to applications

Many applications need flexibility.
The most common ones are traffic avoidance, user preferences, and vehicle restrictions.
Traffic avoidance comes in two forms: Live~\cite{dgpw-crprn-13,dsw-cch-15} and predicted traffic~\cite{ndls-bastd-12,bgsv-mtdtt-13}.
Predicted traffic is often called time-dependent routing.
%
User preferences can vary significantly~\cite{DBLP:conf/gis/FunkeS15,DBLP:conf/gis/DellingGGKTW15,DBLP:conf/gis/FunkeLS16}.
For example, for some users shorter routes are more important than fast routes.
Others want to avoid tunnels or highways.
%
Truck routing differs from car routing due to night driving bans and other restrictions~\cite{kswz-erptd-20}.
%
Flexibility is also often used as building block in multi-agent planning settings~\cite{DBLP:journals/ai/SharonSFS15,DBLP:journals/tciaig/BaierBHH15}.
%
Electric Vehicle Routing also requires flexibility~\cite{DBLP:journals/algorithmica/BaumDPSWZ20,DBLP:conf/aaai/EisnerFS11}.

@@

>>>>

Many applications need flexibility.
The most common ones are traffic avoidance, user preferences, and vehicle restrictions.
Traffic avoidance comes in two forms: Live~\cite{dgpw-crprn-13,dsw-cch-15} and predicted traffic~\cite{ndls-bastd-12,bgsv-mtdtt-13}.
Predicted traffic is often called time-dependent routing.
%
User preferences can vary significantly~\cite{DBLP:conf/gis/FunkeS15,DBLP:conf/gis/DellingGGKTW15,DBLP:conf/gis/FunkeLS16}.
For example, for some users shorter routes are more important than fast routes.
Others want to avoid tunnels or highways.
%
Flexibility is also often used as building block in multi-agent planning settings~\cite{DBLP:journals/ai/SharonSFS15,DBLP:journals/tciaig/BaierBHH15}.
%
Electric Vehicle Routing also requires flexibility~\cite{DBLP:journals/algorithmica/BaumDPSWZ20,DBLP:conf/aaai/EisnerFS11}.

@@

\subsection{Temporary Driving Bans}

Truck routing differs from car routing due to night driving bans and other restrictions.
In~\cite{kswz-erptd-20}, a preliminary version of CH-Potentials is successfully employed to efficiently find routes for trucks when edges may be blocked during certain times, drivers may need to wait at parking locations, and several routes with different trade-offs between arrival time and route quality may need to be considered.
